Using Refactoring Techniques to Reduce Duplication in Object-Oriented Programming Languages\\- Work in Progress -

### 2019-04-24 sattose/paper.tex
Background blah blah

A tool called DCRA (Duplicated Code Refactoring Advisor) looks into refactoring opportunities for clone pairs \cite{fontana2012duplicated}. This tool chooses to only focus on refactoring clone pairs because they argue that \textit{clone pairs are much easier to manage when considered singularly.} As intermidiate steps the authors measure a corpus of Java systems for some clone-related properties of the systems, like the relation between code fragments in a clone pair in terms of inheritance.

>>>>

A tool called DCRA (Duplicated Code Refactoring Advisor) looks into refactoring opportunities for clone pairs \cite{fontana2012duplicated}. This tool chooses to only focus on refactoring clone pairs because they argue that \textit{clone pairs are much easier to manage when considered singularly.} As intermidiate steps the authors measure a corpus of Java systems for some clone-related properties of the systems, like the relation (in terms of inheritance) between code fragments in a clone pair.

Another tool called Aries \cite{higo2004aries, higo2008metric} focuses on the detection of refactoring oriented clones. In this paper the authors describe a few variables by which a clone can be assessed for refactoring suitability. This tool looks however only at the possibility to merge clones, rather than whether clones should be merged. Also, this tool only suggests refactorings, and does not apply them.

There are many other publications that look into code clone refactoring \cite{alwaqfi2017refactoring, chen2018clone, koni2001scenario}. However, none of the publications describing a refactoring tool have published their source code or application for refactoring support. Also, these publications/tools are limited to suggesting refactoring opportunities for clones found, rather than actually applying refactorings where suitable. Furthermore, all of these tools only support a subset of all harmful clones that are found. Furthermore, all published approaches have limitations, for instance false positives when detecting clones \cite{chen2018clone} or being limited to clone pairs \cite{higo2008metric}.

For this research, we strive to improve upon the current state-of-the-art in clone refactoring by building a clone refactoring tool that applies refactorings to a large percentage of clones found. The design decisions for this tool will be made on basis of data gathered from a large corpus of software systems. The tool will be developed on GitHub and stored in the Software Heritage \cite{di2017software} archives to ensure long term preservation. This way we strive to make the problem of duplication in source code easier to deal with.
